Hydra Battles and Cie

### 2021-03-27 doc/chapter-primrec.tex
correction to some coqdoc comments

Thus, the function \texttt{plus} has also type (\texttt{naryFunc 2}).

@@

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Although  the following lemmas are alreday proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec.v},
we wrote alternate proofs in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}%
{Ackermann.MoreAck.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

We alreday proved that \texttt{S} is \texttt{PR 1}, but we need to consider a function of three arguments, which ignores its first and third arguments.
Fortunately, the library \texttt{primRec} already contains lemmas adapted to this kind of situation.

@@

Thus, our first subgoal is solved easily and the proof ends, applying alreday proven lemmas.

>>>>

\begin{Coqsrc}
Check plus: naryFunc 2.

Check 42: naryFunc 0.

Check (fun n p q : nat =>  n * p + q): naryFunc 3.
\end{Coqsrc}

@@

The constructors \texttt{zeroFunc}, \texttt{succFunc},  and \texttt{projFunc} of type
\texttt{PrimRec} allows us to write trivial proofs of primitive recursivity. 
Although  the following lemmas are already proven in 
\href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec.v},
we wrote alternate proofs in 
\href{../theories/html/hydras.MoreAck.PrimRecExamples.html}%
{Ackermann.MoreAck.PrimRecExamples.v}, in order to illustrate the main proof patterns.

@@

We already proved that \texttt{S} is \texttt{PR 1}, but we need to consider a function of three arguments, which ignores its first and third arguments.
Fortunately, the library \texttt{primRec} already contains lemmas adapted to this kind of situation.

@@

Thus, our first subgoal is solved easily and the proof ends, applying already proven lemmas.
